---
title: "Trinity Main Code"
author: "Albert Ding, Xiangliang Liu, Emma Zhang"
date: "April 11, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###loading all the library
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(maps)
library(Hmisc)
library(ipw)
library(arm)
library(randomForest)
library(e1071)
library(mlbench)
library(caret)
library(glmnet)
library(kableExtra)
library(texreg)
```

##Read in all the data in MM
```{r}
# MM_tblClaim <- read.delim(file = "F:/Boston University/Raw Data/Spring 2019/MM/MM Sample/MM_tblClaim.txt.gz",header = TRUE,sep="|")
# MM_tblClaimICD <- read.delim(file = "F:/Boston University/Raw Data/Spring 2019/MM/MM Sample/MM_tblClaimICD.txt.gz",header = TRUE,sep="|")
# MM_tblEnrollment <- read.delim(file = "F:/Boston University/Raw Data/Spring 2019/MM/MM Sample/MM_tblEnrollment.txt.gz",header = TRUE,sep="|")
# MM_tblNPIClaimXref <- read.delim(file = "F:/Boston University/Raw Data/Spring 2019/MM/MM Sample/MM_tblNPIClaimXref.txt.gz",header = TRUE,sep="|")
# MM_tblPatient <- read.delim(file = "F:/Boston University/Raw Data/Spring 2019/MM/MM Sample/MM_tblPatient.txt.gz",header = TRUE,sep="|")
# MM_tblRevenue <- read.delim(file = "F:/Boston University/Raw Data/Spring 2019/MM/MM Sample/MM_tblRevenue.txt.gz",header = TRUE,sep="|")

#save.image(file = "F:/BU Users/Team3/data/Alldata.RData")


```

##Clean the data:
```{r eval=FALSE, include=FALSE}
#change the ICD9 version to ICD10 version
ICD9 = filter(MM_tblClaimICD,Code_Version == 9)
ICD9MM = filter(ICD9, ICD_Code %in% c(20302,20301))
ICD9MM$ICD_Code[ICD9MM$ICD_Code ==20302] <- "C9002"
ICD9MM$ICD_Code[ICD9MM$ICD_Code ==20301] <- "C9001"
IDC9_final<-ICD9MM %>% dplyr::select(TPI_Claim_Id,Patient_ID,Data_Set,ICD_Code,DGNS_Source,Code_Flag)
#data cleaning in ICD10
ICD10 = filter(MM_tblClaimICD, Code_Version ==10)
ICD10MM = filter(ICD10, ICD_Code %in% c("C9001","C9002"))
IDC10_final <- ICD10MM %>% dplyr::select(TPI_Claim_Id,Patient_ID,Data_Set,ICD_Code,DGNS_Source,Code_Flag)
#merge ICD9 and ICD10 together.
ICD <- bind_rows(IDC10_final,IDC9_final)
ICD_final <-filter(ICD, DGNS_Source == "Diagnosis")
ICD_final<- ICD_final[!duplicated(ICD_final$TPI_Claim_Id),]
#nrow(ICD_final)
length(unique(MM_tblClaim$TPI_Claim_Id))
MM_tbl_Claim <- dplyr::select(MM_tblClaim, TPI_Claim_Id,Patient_ID, Service_Year, Facility_Type_Code, Facility_Type_Description,Claim_Type_Code,Claim_Type_Description, Facility_Type_Code, Facility_Type_Service_Description)
MM_claim<-left_join(ICD_final,MM_tbl_Claim, by= "TPI_Claim_Id")

#change the column name of patient_id in patient level
colnames(MM_claim)[colnames(MM_claim) =="Patient_ID.x"]<- "Patient_ID"
#check whether the patient ID is unique.
length(unique(MM_tblPatient$Patient_ID))
# As we can see the patient Id is not unique.
#Select the column in patient level
MM_tbl_Patient <-dplyr::select(MM_tblPatient, Service_Year,Patient_ID,Census_Bureau_Region, State,AGE,Sex, Race, Date_Of_Death, Year_Of_Death, MEDICARE_STATUS_CODE,MEDICARE_STATUS, ORIG_REASON_FOR_ENTITLEMENT, CURR_REASON_FOR_ENTITLEMENT,IP,PO,OP )
Patient_MM <- filter(MM_tbl_Patient,Patient_ID %in% ICD_final$Patient_ID)
#merge the dataset, MM_data_raw is the claim level of data
MM_data_raw<- merge(MM_claim,MM_tbl_Patient, by = c("Patient_ID", "Service_Year"))

#select the treatment variable in revenue dataset
revenue <-  MM_tblRevenue%>%dplyr::select(TPI_Claim_Id,Patient_ID,Service_Year,Srvc_From_Date,Srvc_Thru_Date,Provider_Type,Revenue_Center_Code,HCPCS_Or_CPT_Code,HCPCS_Or_CPT_Code_Desc)

#intergrate all the treatment for MM Patient with unique treatment.
Treatment_MM <- left_join( MM_data_raw,revenue, by = "TPI_Claim_Id")
#Treatment_MM is the final version of the data,each row is a treatment.

#save.image(file = "F:/BU Users/Team3/data/complete.RData")

```



#Calculate the number of remission and relapse in firs-line treatment
```{r}
load("complete.Rdata")

# Convert date format in MM_Revenue
Treatment_MM$Srvc_Thru_Date<-gsub("-","",Treatment_MM$Srvc_Thru_Date)
Treatment_MM$Srvc_Thru_Date<-as.Date(Treatment_MM$Srvc_Thru_Date, "%Y%m%d")


# Select the first line treatment with relapse
First_treatment_relapse<-Treatment_MM%>%
  filter(ICD_Code =="C9002")%>%
  group_by(Patient_ID.x)%>%
  summarise(relapse_date = min(Srvc_Thru_Date))


#leftjoin the table for patients who ever remiss.
First_relapse <-left_join(Treatment_MM, First_treatment_relapse, by = "Patient_ID.x")
first_treatment_rel <- filter(First_relapse, Srvc_Thru_Date< relapse_date )

#Create a indicator variable "rem_relapse"
first_treatment_rel$rem_relapse <- 1

# Select the first line treatment with remission
first_treatment_rem<-Treatment_MM%>%
  filter(ICD_Code =="C9001" & ! Patient_ID.x %in% First_treatment_relapse$Patient_ID.x)

#Create a indicator variable "rem_relapse"
first_treatment_rem$rem_relapse <- 0


#bind rowws together
First_treatment <- bind_rows(first_treatment_rel, first_treatment_rem)
First_treatment <- filter(First_treatment, HCPCS_Or_CPT_Code !="")#filter all the HCPCS/CPT code is blank
First_treatment$rem_relapse <- as.factor(First_treatment$rem_relapse) 
First_treatment$Service_Year.x <- as.factor(First_treatment$Service_Year.x)



```

##Check the missingness:
```{r}
missing<-First_treatment %>% summarise_all(funs(sum(is.na(.))/n()*100)) %>%
gather(key="feature", value="missing_pct")
missing%>%
ggplot(aes(x=reorder(feature,-missing_pct),y=missing_pct)) +
geom_bar(stat="identity", fill="sky blue")+
labs(y = "missing %", x = "features") +
coord_flip() +
labs(title = "proportion of missing value in the dataset")
```

###Feature engineering: Select useful treatment that influence the model

##draw a map of demographic info
```{r}
#Construct a dataframe with number of claim in state
a <-MM_data_raw%>%
  group_by(State)%>%
  summarise(n = n())
colnames(a)[colnames(a)== "State"] <- "region"
a$region <- as.character(a$region)
#Construct a dataframe with number of MM patient in state
b <-Patient_MM%>%
  group_by(State)%>%
  summarise(n = n())
colnames(b)[colnames(a)== "State"] <- "region"
b$region <- as.character(a$region)
#Load the US map data
us_states <- map_data("state")
us_states$region <- capitalize(us_states$region)
Claim_states <- left_join(us_states,a, by ="region")
Patient_states <- left_join(us_states,b, by ="region")
library(maps)
library(Hmisc)
#map 1
ggplot(data = Claim_states, aes(x = long, y = lat, group =group, fill = n)) + geom_polygon(color = "grey90",size = 0.1)+ coord_map(projection = "albers", lat0 =39,lat1 = 45)+ labs(fill = "Numbers of Claims") +labs(title ="Number of MM Claims in Different States",x="Longtitude",y="Latitude")
#save.image(file = "F:/BU Users/Team3/data/complete.RData")
#map 2
ggplot(data = Patient_states, aes(x = long, y = lat, group =group, fill = n)) + geom_polygon(color = "grey90",size = 0.1)+ coord_map(projection = "albers", lat0 =39,lat1 = 45)+ labs(fill = "Numbers of Patients") +labs(title ="Number of MM patients in Different States",x="Longtitude",y="Latitude")

```

####manually selected features

```{r}
typical<-filter(First_treatment, HCPCS_Or_CPT_Code %in% c("J9041","J9047","J9070","J8530","J9145","J9476","J8540","J1100","J1650","J1442","Q5101","J1442","J1441","J2505","J1440","J2270","J2275","J2430","J2562","38241","J3489","J3487") )

typical_treatment <-typical %>% 
  mutate(bortezomib =ifelse(HCPCS_Or_CPT_Code =="J9041",1,0))%>%
  mutate(carfilzomib =ifelse(HCPCS_Or_CPT_Code =="J9047",1,0))%>%
  mutate(cyclophosphamide =ifelse(HCPCS_Or_CPT_Code %in% c("J9070","J8530"),1,0))%>%
  mutate(daratumumab =ifelse(HCPCS_Or_CPT_Code %in% c("J9145","JC9476"),1,0))%>%

  mutate(dexamethasone =ifelse(HCPCS_Or_CPT_Code %in% c("J8540","J1100"),1,0))%>%

  mutate(enoxaparin =ifelse(HCPCS_Or_CPT_Code =="J1650",1,0))%>%
  mutate(filgrastim =ifelse(HCPCS_Or_CPT_Code %in% c("J1442","Q5101","J1442","J1441","J2505","J1440"),1,0))%>%
  mutate(morphine_sulfate =ifelse(HCPCS_Or_CPT_Code %in% c("J2270","J2275"),1,0))%>%
  mutate(pamidronate = ifelse(HCPCS_Or_CPT_Code == "J2430",1,0))%>%
  mutate(plerixafor = ifelse(HCPCS_Or_CPT_Code == "J2562",1,0))%>%
  mutate(stem_cell_transplant = ifelse(HCPCS_Or_CPT_Code == "38241",1,0))%>%
  mutate(zoledronic_acid = ifelse(HCPCS_Or_CPT_Code %in% c("J3489","J3487"),1,0))

typical_treatment$treatment[typical_treatment$HCPCS_Or_CPT_Code=="J9041"] = "bortezomib"
typical_treatment$treatment[typical_treatment$HCPCS_Or_CPT_Code=="J9047"] = "carfilzomib"
typical_treatment$treatment[typical_treatment$HCPCS_Or_CPT_Code %in% c("J9070","J8530")] = "cyclophosphamide"
typical_treatment$treatment[typical_treatment$HCPCS_Or_CPT_Code %in% c("J9145","JC9476")] = "daratumumab"
typical_treatment$treatment[typical_treatment$HCPCS_Or_CPT_Code %in% c("J8540","J1100")] = "dexamethasone"
typical_treatment$treatment[typical_treatment$HCPCS_Or_CPT_Code=="J1650"] = "enoxaparin"
typical_treatment$treatment[typical_treatment$HCPCS_Or_CPT_Code %in% c("J1442","Q5101","J1442","J1441","J2505","J1440")] = "filgrastim"
typical_treatment$treatment[typical_treatment$HCPCS_Or_CPT_Code %in% c("J2270","J2275")] = "morphine_sulfate"
typical_treatment$treatment[typical_treatment$HCPCS_Or_CPT_Code=="J2430"] = "pamidronate"
typical_treatment$treatment[typical_treatment$HCPCS_Or_CPT_Code=="J2562"] = "plerixafor"
typical_treatment$treatment[typical_treatment$HCPCS_Or_CPT_Code=="38241"] = "stem_cell_transplant"
typical_treatment$treatment[typical_treatment$HCPCS_Or_CPT_Code %in% c("J3489","J3487")] = "mzoledronic_acid"

patient_typical <- dplyr::select(typical_treatment,2,3,12, 20,24,25,26,33,35,37:50)
patient_typical$Service_Year.x <- as.character(patient_typical$Service_Year.x)
patient_level<-patient_typical%>%
  group_by(Patient_ID.x,Service_Year.x,Data_Set, AGE, Race, Sex,rem_relapse,treatment)%>%
  summarise(bortezomib = sum(bortezomib),
    carfilzomib = sum(carfilzomib),
    cyclophosphamide = sum(cyclophosphamide),
    daratumumab = sum(daratumumab),
    dexamethasone = sum(dexamethasone),
    enoxaparin = sum(enoxaparin),
    filgrastim = sum(filgrastim),
    morphine_sulfate = sum(morphine_sulfate),
    pamidronate = sum(pamidronate),
    plerixafor = sum(plerixafor),
    stem_cell_transplant = sum(stem_cell_transplant),
    zoledronic_acid = sum(zoledronic_acid))


patient_typical$Service_Year.x <- as.character(patient_typical$Service_Year.x)
```



##EDAs
```{r}
#EDAs regarding to demographic info for all patients
ggplot(data = Patient_MM, aes(x = AGE )) + geom_histogram(fill= "sky blue",bins = 50)+theme_classic()+labs(title="The distribution of MM Patient in Different Age", x="Age",y="Number of Patient")

ggplot(data =Patient_MM, aes(x = AGE )) + geom_histogram(fill= "sky blue")+theme_classic()+labs(title="The distribution of MM Patient in Different Age", x="Age",y="Number of Patient")

ggplot( Patient_MM, aes(x = Sex,fill = Sex)) + geom_bar()+ theme_classic()+labs(title="The Number of MM Patients In Different Gender",x="Sex",y="Number of Patient")
Patient_MM<-Patient_MM%>%
  filter(Race != "")

ggplot( patient_level[patient_level$Race!="",], aes(x = Race,fill= Race)) + geom_bar()+ theme_classic()+labs(title="Number of Patients in Different Race",y="Number of Patients")+theme(axis.text.x = element_text(angle = 90))
ggplot( Patient_MM, aes(x =Census_Bureau_Region,fill= Race)) + geom_bar()+ theme_classic()+labs(title="The Number of MM Patients in Different Region",y="Number of Patients")

ggplot( MM_data_raw, aes(x = ICD_Code,fill = ICD_Code )) + geom_bar()+ theme_classic()+labs(title="The Number of MM Patients relaps and remission in Different Years",y="Number of Patients relaps and remission")+ facet_grid(cols = vars(Service_Year))

#type of treatments that used previously
ggplot( typical_treatment, aes(x = HCPCS_Or_CPT_Code,fill= as.factor(Service_Year.x))) + geom_bar()+ theme_classic()+labs(title="The Number of traeatment in Different Years",y="Number of Treatment")

#find the highest frequency of first-line treatments:

treat1 <-typical_treatment%>%
  group_by(treatment)%>%
  summarise(n = n())%>%
  arrange(desc(n))
treat1 <- mutate(treat1, proportion = n/nrow(typical_treatment))

treat2 <-patient_level%>%
  group_by(treatment)%>%
  summarise(n = n())%>%
  arrange(desc(n))
colnames(treat2)[colnames(treat2)=="n"]<-"n_patient"
treat <- left_join(treat1, treat2, by = "treatment")


ggplot(data = typical_treatment, aes(as.factor(rem_relapse), fill =as.factor(rem_relapse)))+ geom_bar() + theme(axis.text.x  = element_text(angle = 00, hjust =1)) + facet_wrap(vars(Service_Year.x)) + labs( x = "remission or relapse", title = "The number of patients relapse or remit in different years",fill = "Relapse or not")

ggplot(data = typical_treatment, aes(as.factor(rem_relapse), fill =as.factor(rem_relapse)))+ geom_bar() + theme(axis.text.x  = element_text(angle = 00, hjust =1)) + facet_wrap(vars(Data_Set)) + labs( x = "remission or relapse", title = "The number of patients relapse or remit in different data set",fill = "Relapse or not")

ggplot(data = typical_treatment, aes(as.factor(rem_relapse), fill =as.factor(rem_relapse)))+ geom_bar() + theme(axis.text.x  = element_text(angle = 00, hjust =1)) + facet_wrap(vars(Claim_Type_Description)) + labs( x = "remission or relapse", title = "The number of patients relapse or remit in different claim type",fill = "Relapse or not")

abcd <- left_join(typical_treatment, treat, by = "treatment") 

ggplot(data = abcd, aes(reorder(treatment,-n), fill = as.factor(rem_relapse)))+ geom_bar(position = "fill") +theme(axis.text.x  = element_text(angle = 90, hjust =1)) +labs( x = "Patient Group with One or More of Stated Treatment (Non-Disjoint)",y = "Proportion Remission and Relapse", title = "Proportion Remission or Relapse for Patient Group \n Exposed to One or More of Corresponding Treatment",fill = "Relapse or Not") + theme(plot.title = element_text(hjust = 0.5))

kable(treat)

ggplot(data = patient_level, aes(as.factor(rem_relapse), fill = as.factor(rem_relapse))) + geom_bar()+labs( x = "remission or relapse", title = "The number of patients relapse or remit",fill = "Relapse or not")

ggplot(patient_level, aes(x = as.factor(rem_relapse), y =AGE, color = as.factor(rem_relapse))) + geom_boxplot()+labs (x = "remission or relapse", title = "distribution of age for patients with relapse of remission",fill = "Relapse or not") + scale_fill_discrete(name = "relapse or not")

ggplot(patient_level,aes(Sex,fill = as.factor(rem_relapse))) + geom_bar(position = "fill")+labs (x = "Remission or Relapse",y= "Proportion Remission and Relapse", title = "Proportion of Relapse and Remission Patients with Gender",fill = "Relapse or Not")
# ggplot(data = First_treatment, aes(as.factor(rem_relapse,), fill =as.factor(rem_relapse)))+ geom_bar() +theme(axis.text.x  = element_text(angle = 0, hjust =1) )+ facet_wrap(vars(Facility_Type_Description))+labs(title = "Distribution of treatment resualt in different facilities", x = "ICD code")+labs( x = "remission or relapse", title = "The number of patients relapse or remit in different ",fill = "Relapse ,or not")


```

###modeling (random forest, logistics)
```{r}
#using varImp() fucntion
library(caret)
#using random forest to find the importance of varible
set.seed(1)
patient_level <-patient_level[,-8]
patient_level_1 <- patient_level[,-1]
patient_level_1$rem_relapse <- as.factor(patient_level_1$rem_relapse)
training.samples <- patient_level_1$rem_relapse %>% 
  createDataPartition(p = 0.6, list = FALSE)
train.data  <- patient_level_1[training.samples, ]
test.data <- patient_level_1[-training.samples, ]
        
rf_mod <- randomForest(rem_relapse ~ ., data =train.data ,ntree = 1000)
varImpPlot(rf_mod)

#ROC
require(pROC)
rf.roc<-roc(train.data$rem_relapse,rf_mod$votes[,2])
plot(rf.roc)
auc(rf.roc)

y_hat_rf1 <- predict(rf_mod, newdata = test.data )
# Model accuracy
observed <-test.data$rem_relapse
predicted <-y_hat_rf1
mean(predicted == observed)
table(observed,predicted)


#using grid search to find the best mtry

set.seed(1)
control <- trainControl(method="repeatedcv", number=10, repeats=3, search="random")
tunegrid <- expand.grid(.mtry=c(1:15))
rf_gridsearch <- train(rem_relapse~., data=patient_level_1, method="rf", metric="Accuracy", tuneGrid=tunegrid, trControl=control)
kable(print(rf_gridsearch))
plot(rf_gridsearch)

# # Manual Search best ntreee(we don't have to consider the number of trees.)
# control <- trainControl(method="repeatedcv", number=10, repeats=3, search="grid")
# tunegrid <- expand.grid(.mtry=c(sqrt(ncol(patient_level_1))))
# modellist <- list()
# for (ntree in c(1000, 1500, 2000, 2500)) {
# 	set.seed(1)
# 	fit <- train(rem_relapse~., data=patient_level_1, method="rf", metric="Accuracy", tuneGrid=tunegrid, trControl=control, ntree=ntree)
# 	key <- toString(ntree)
# 	modellist[[key]] <- fit
# }
# # compare results
# results <- resamples(modellist)
# summary(results)
# dotplot(results)

##set a indicator for whether the treatment was used

# patient_level2<-patient_typical%>%
#   group_by(Patient_ID.x,Service_Year.x,Data_Set, AGE, Race, Sex,rem_relapse)%>%
#   summarise(bortezomib = sum(bortezomib),
#     carfilzomib = sum(carfilzomib),
#     cyclophosphamide = ifelse(sum(cyclophosphamide)>=1,1,0),
#     daratumumab = ifelse(sum(daratumumab)>=1,1,0),
#     denosumab = ifelse(sum(denosumab)>=1,1,0),
#     dexamethasone = ifelse(sum(dexamethasone)>=1,1,0),
#     elotuzumab = ifelse(sum(elotuzumab)>=1,1,0),
#     enoxaparin = ifelse(sum(enoxaparin)>=1,1,0),
#     filgrastim = ifelse(sum(filgrastim)>=1,1,0),
#     melphalan = ifelse(sum(melphalan)>=1,1,0),
#     morphine_sulfate = ifelse(sum(morphine_sulfate)>=1,1,0),
#     pamidronate = ifelse(sum(pamidronate)>=1,1,0),
#     plerixafor = ifelse(sum(plerixafor)>=1,1,0),
#     prednisone= ifelse(sum(prednisone)>=1,1,0),
#     prednisone= ifelse(sum(prednisone)>=1,1,0),
#     stem_cell_transplant = ifelse(sum(stem_cell_transplant)>=1,1,0),
#     zoledronic_acid = ifelse(sum(zoledronic_acid)>=1,1,0))
# 
# patient_level_1 <- patient_level2[,-1]
# patient_level_1$rem_relapse <- as.factor(patient_level_1$rem_relapse)
# training.samples <- patient_level_1$rem_relapse %>% 
#   createDataPartition(p = 0.6, list = FALSE)
# train.data  <- patient_level_1[training.samples, ]
# test.data <- patient_level_1[-training.samples, ]
#         
# rf_mod <- randomForest(rem_relapse ~ ., data =train.data ,ntree = 1000)
# varImpPlot(rf_mod)
# #ROC
# require(pROC)
# rf.roc<-pROC::roc(train.data$rem_relapse,rf_mod$votes[,2])
# plot(rf.roc)
# auc(rf.roc)
# 
# y_hat <- predict(rf_mod, newdata = test.data )
# # Model accuracy
# mean(y_hat == test.data$rem_relapse)
# table(test.data$rem_relapse,y_hat)
# 
# nrow(patient_level_1)


#logistic mode
logit_mod <- glm(as.factor(rem_relapse) ~., family = binomial(link = "logit"),data =train.data)
summary(logit_mod)
screenreg(logit_mod, custom.model.names = "logistics model")

#binned plot
y_hat_log <- predict(logit_mod, newdata = test.data)
predicted <- ifelse(y_hat_log >0.5,1,0)
observed <- test.data$rem_relapse
mean(predicted == observed)
table(predicted,observed)

binnedplot(fitted(logit_mod), resid(logit_mod))

```


###CPT method models(random forest 2 and logistics model)
```{r}
set.seed(1234)
#filter all the treatment inside 
Catagory<-filter(First_treatment, HCPCS_Or_CPT_Code %in% c(10000:69990,90281:99099,99151:99199,99500:99607))
CPT_level<-filter(Catagory, HCPCS_Or_CPT_Code %in% c("96401","38221","96409","96413"))
# treat_catagory <-Catagory%>%
#   group_by(HCPCS_Or_CPT_Code)%>%
#   summarise(n = n())%>%
#   arrange(desc(n))
# 
# treat_c <- mutate(treat_catagory, proportion = n/nrow(Catagory))

CPT_treatment <-CPT_level %>% 
  mutate(chemo_anti_neopl =ifelse(HCPCS_Or_CPT_Code =="96401",1,0))%>%
  mutate(bone_marrow_biopsy =ifelse(HCPCS_Or_CPT_Code =="38221",1,0))%>%
  mutate(chemo_iv_push =ifelse(HCPCS_Or_CPT_Code =="96409",1,0))%>%
  mutate(chemo_iv_infusion =ifelse(HCPCS_Or_CPT_Code =="96413",1,0))

 CPT_typical<-dplyr::select(CPT_treatment,2,3,12, 20,24,25,26,33,35,37:41)
 CPT_typical$Service_Year.x <- as.character(CPT_typical$Service_Year.x)
 CPT_level<-CPT_typical%>%
  group_by(Patient_ID.x,Service_Year.x,Data_Set, AGE, Race, Sex,rem_relapse)%>%
  summarise(chemo_anti_neopl = sum(chemo_anti_neopl),
    bone_marrow_biopsy = sum(bone_marrow_biopsy),
    chemo_iv_push = sum(chemo_iv_push),
    chemo_iv_infusion = sum(chemo_iv_infusion))
#define testing data dn training data
 CPT_level_1 <- CPT_level[,-1]
CPT_level_1$rem_relapse <- as.factor(CPT_level_1$rem_relapse)
training.samples <- CPT_level_1$rem_relapse %>% 
  createDataPartition(p = 0.6, list = FALSE)
train.data  <- CPT_level_1[training.samples, ]
test.data <- CPT_level_1[-training.samples, ]
        
#logistic mode
logit_mod_2 <- glm(rem_relapse ~., family = binomial(link = "logit"),data =train.data)
summary(logit_mod_2)
y_hat_log2 <- predict(logit_mod_2, newdata = test.data )
predicted.classes <- ifelse(y_hat_log2>0.5,1,0)
observed.classes <- test.data$rem_relapse
#accuracy rate
mean(predicted.classes == observed.classes)
table(predicted.classes, observed.classes)
#binned plot 
binnedplot(fitted(logit_mod_2), resid(logit_mod_2))
#random forest 2 model 

rf_mod_2 <- randomForest(rem_relapse ~ ., data =train.data ,ntree = 1000)
varImpPlot(rf_mod_2)
#ROC
require(pROC)
rf.roc<-roc(train.data$rem_relapse,rf_mod_2$votes[,2])
plot(rf.roc)
auc(rf.roc)

y_hat_2 <- predict(rf_mod_2, newdata = test.data )
predicted.classes <- y_hat_2
observed.classes <- test.data$rem_relapse
# Model accuracy
mean(predicted.classes == observed.classes)
table(predicted.classes,observed.classes)
```




##lasso/ridge regression model

```{r}
#ridge lasso logistics regression
set.seed(2019)
# Split the data into training and test set
patient_level_1$rem_relapse <- as.factor(patient_level_1$rem_relapse)
training.samples <- patient_level_1$rem_relapse %>% 
  createDataPartition(p = 0.6, list = FALSE)
train.data  <- patient_level_1[training.samples, ]
test.data <- patient_level_1[-training.samples, ]
# Dumy code categorical predictor variables
x <- model.matrix(rem_relapse~., train.data)[,-1]
# Convert the outcome (class) to a numerical variable
y <- train.data$rem_relapse
cv_log <-glmnet(x, y, family = "binomial", alpha = 1, lambda = NULL)

# Find the best lambda using cross-validation
set.seed(123) 
cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")
# Fit the final model on the training data
model <- glmnet(x, y, alpha = 1, family = "binomial", lambda = cv.lasso$lambda.min)
# Display regression coefficients
coef(model)
# Make predictions on the test data

x.test <- model.matrix(rem_relapse~., test.data)[,-1]
predict <- model %>% predict(newx = x.test)
predicted <- ifelse(predict> 0.5,1,0)
#confusion matrix
observed<- test.data$rem_relapse
table(predicted,observed)
# Model accuracy
mean(predicted == observed)

```

###Ridge regression
```{r}

set.seed(123)
# Split the data into training and test set
patient_level_1$rem_relapse <- as.factor(patient_level_1$rem_relapse)
training.samples <- patient_level_1$rem_relapse %>% 
  createDataPartition(p = 0.5, list = FALSE)
train.data  <- patient_level_1[training.samples, ]
test.data <- patient_level_1[-training.samples, ]
# Dumy code categorical predictor variables
x <- model.matrix(rem_relapse~., train.data)[,-1]
# Convert the outcome (class) to a numerical variable
y <- train.data$rem_relapse
cv_log <-glmnet(x, y, family = "binomial", alpha = 0, lambda = NULL)

# Find the best lambda using cross-validation
set.seed(123) 
cv.lasso <- cv.glmnet(x, y, alpha = 0, family = "binomial")
cv.lasso$lambda.min
# Fit the final model on the training data
model <- glmnet(x, y, alpha = 0, family = "binomial", lambda = cv.lasso$lambda.min)
# Display regression coefficients
summary(model)
# Make predictions on the test data

x.test <- model.matrix(rem_relapse~., test.data)[,-1]
predict <- model %>% predict(newx = x.test)
predicted <- ifelse(predict> 0.5,1,0)
#confusion matrix
observed<- test.data$rem_relapse
table(predicted,observed)
# Model accuracy
mean(predicted == observed)
```

###XGBoosting
```{r eval=FALSE, include=FALSE}
require(xgboost)
head(train.data)
#select the train dataset and traser it to matrix
train_data$outcome<-ifelse(train_data$ICD_Code =="C9001", 1, 0)
input_train<-as.matrix(train.data[,-c(1,2,4,5)])
output_train<-as.matrix(train.data[,9])
#dtrain <- xgb.DMatrix(train$rem_relapse, label=y)
#dtest <- xgb.DMatrix(data = test$data, label=test$label),eval_metric = "auc"
bst <- xgboost(data =input_train, label=output_train,max.depth = 2, eta = 1, nthread = 2, nrounds = 2, objective = "binary:logistic",eval_metric = "auc")
xgb.probs<-predict(bst, input_train)
hist(xgb.probs)
cv.fit<-xgb.cv(max_depth = 2, eta = 1, data = input_train,
               label = output_train, metrics = "auc", nfold = 10,
               nrounds = 50, objective ="binary:logistic")
best_param = list()
best_seednumber = 1234
best_logloss = Inf
best_logloss_index = 0


for (iter in 1:1000) {
  param <-list(objective = "binary:logistic",
               eval_metric = "mlogloss",
               max_depth = sample(6:10, 1),
               eta = runif(1,0.01,0.3),
               gamma = runif(1,0.0,0.2),
               subsample = runif(1,0.6,0.9),
               colsample_bytree = runif(1,0.5,0.8),
               min_child_weight = sample(1:40, 1),
               max_delta_depth = sample(1:10, 1)
               )
  cv.nround = 1000
  cv.nfold = 5
  seed.number = sample.int(10000,1)[[1]]
  set.seed(seed.number)
  mdcv<-xgb.cv()
}
```
